Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-01 ms/manuscript.Rmd
Update MS
use bookdown instead of officedown. couldn't get template to work.

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
bibliography: 
  - references.yaml
  - references_other.yaml
output: 
  officedown::rdocx_document:
    base_format: bookdown::word_document2
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    toc: no
    reference_num: false
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries used for rendering Rmds
library(officedown)
library(officer)
library(flextable)
library(kableExtra)
library(ftExtra)
library(patchwork)

@@

<!-- Remove page numbers -->
\pagenumbering{gobble}

@@

Joel H. Nitta^1^, Brent D. Mishler^2^, Wataru Iwasaki^1^, and Atsushi Ebihara^3^

^1^Department of Biological Sciences, Graduate School of Science, The University of Tokyo, 2-11-16 Yayoi, Bunkyo-ku, Tokyo 113-0032, Japan

^2^University and Jepson Herbaria, University of California, Berkeley, CA 94720‐2465, USA

^3^Department of Botany, National Museum of Nature and Science, 4-1-1 Amakubo, Tsukuba-shi, Ibaraki, 305-0005, Japan

@@

**Aim** To characterize multiple facets of biodiversity and understand how these relate to bioregions and conservation status.

@@

**Main conclusions** The integrative approach used here reveals previously undetected patterns of biodiversity in the ferns of Japan. The different distributions of each diversity type reflect the major bioregions. Although peak areas of different diversity types are largely non-overlapping, each one has a relatively high protection status. Despite this, future conservation efforts must be cognizant of dangers not addressed here such as climate change and herbivory by deer.

@@

All measures of biodiversity and CANAPE were carried out using the `r pack("canaper")` package (https://github.com/joelnitta/canaper), which calculates observed values of biodiversity using functions in the `r pack("phyloregion")` package [@Daru2020a] and randomizations using the `r pack("picante")` package [@Kembel2010].

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
bibliography: 
  - references.yaml
  - references_other.yaml
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries used for rendering Rmds
# library(officedown)
# library(officer)
library(flextable)
library(kableExtra)
library(ftExtra)
library(patchwork)

@@

@@

Short running title: Biodiversity of Japanese ferns

Joel H. Nitta^1^, Brent D. Mishler^2^, Wataru Iwasaki^1, 3, 4, 5, 6^, and Atsushi Ebihara^7^

^1^Department of Biological Sciences, Graduate School of Science, The University of Tokyo, Tokyo, Japan

^2^University and Jepson Herbaria, University of California, Berkeley, CA, USA

^3^Department of Computational Biology and Medical Sciences, Graduate School of Frontier Sciences, The University of Tokyo, Kashiwa, Japan

^4^Atmosphere and Ocean Research Institute, The University of Tokyo, Kashiwa, Japan

^5^Institute for Quantitative Biosciences, The University of Tokyo, Tokyo, Japan

^6^Collaborative Research Institute for Innovative Microbiology, The University of Tokyo, Tokyo, Japan

^7^Department of Botany, National Museum of Nature and Science, Tsukuba, Japan

@@

**Aim** To characterize multiple facets and drivers of biodiversity and understand how these relate to bioregions and conservation status.

@@

**Main conclusions** The integrative approach used here reveals previously undetected patterns and drivers of biodiversity in the ferns of Japan. The different distributions of each diversity type reflect the major bioregions. Although peak areas of different diversity types are largely non-overlapping, each one has a relatively high protection status. Despite this, future conservation efforts must be cognizant of dangers not addressed here such as climate change and herbivory by deer.

@@

All measures of biodiversity and CANAPE were carried out using the `r pack("canaper")` package (https://github.com/joelnitta/canaper), which calculates raw biodiversity metrics using functions in the `r pack("phyloregion")` package [@Daru2020a] and randomizations using the `r pack("picante")` package [@Kembel2010].
